Effects of Unemployment Benefits and Uncertainty in Heterogeneous Models

### 2017-01-21 presentation/presentation.tex
Copied graphs into image folder, started ẃorking on presentation

% Section and subsections will appear in the presentation overview
% and table of contents.
\section{Part I}
\subsection{}
\begin{frame}{Motivation}
  \begin{itemize}

  \item {
  Item 1
  }

  \item {
  Item 2  
  }

  \item {
  Item 3
  }
  \end{itemize}

  \centering{\includegraphics[scale=0.30]{eq18}}
\end{frame}

\section{Part II}
\subsection{}

@@

\begin{frame}{Adding aggregate uncertainty}
  \begin{itemize}

  \item {
  Aggregate uncertainty! Why?
  }
  \pause
  \item {
  Two aggregate productivity : $z \in \{ 0.99, 1.01 \}$.
  }

  \item {
  Two unemployment states: $L \in \{ 0.1, 0.4 \}$.
  }

  \item {
  2 transition matricies between employed and unemployed respectively in good and bad states and 1 transition matrix between good and bad state: $L \in \{ 0.1, 0.4 \}$.
  }

  \pause

  \item {
  Let's solve it!.
  }

  \end{itemize}

\end{frame}

\begin{frame}{Problem}
  \begin{itemize}

  \item {
  The introduction of aggregate uncertainty makes the distribution of wealth changing over time, which is infinite dimensional object.
  }

  \item {
  The capital distribution must be taken into account by the agents, therefore it becomes state variable.
  }

  \end{itemize}

\end{frame}

\begin{frame}{Solution}
  \begin{itemize}

  \item {
  There is no solution.
  }

  \item {
  Krusell and Smith (1997) suggest an algorithm to solve the issue by an approximation, which could be summerized as "rational adaptive expectations".
  }

  \item {
  They assume that the agents forecast prices by using the future mean of the wealth distribution.
  }

  \item {
  The actual forecast is made for the future mean based on previous realizations using some Least Squares technique.
  }

  \end{itemize}

\end{frame}

\begin{frame}{Algorithm}
  \begin{enumerate}

  \item {
  Draw shocks.
  }

  \item {
  Guess initial coefficients for the forcasting rule.  
  }

  \item {
  Solve the individual problem.
  }

  \item {
  Use the policy function to generate a sequence of capital distributions.
  }

  \item {
  The actual forecast is made for the future mean based on previous realizations using some Least Squares technique.
  }

  \item {
  Estimate new coefficients based on past realizations of the distribution and iterate until they converge. 
  }

  \end{enumerate}

\end{frame}

>>>>

% Section and subsections will appear in the presentation overview
% and table of contents.
\section{Part I}
\subsection{}
\begin{frame}{Introduction}
  \begin{itemize}

  \item {1.}
  \end{itemize}
\end{frame}
\section{Part II}
\subsection{}
\begin{frame}{Welfare Measurement}
  \begin{itemize}
  \item {
  Which variable should we look at if we want to say consumers are better off? Output? Consumption?
  }
  \item {
  We want to measure somehow whether consumer welfare increased or not.
  }
  \item {
  But how to measure welfare? Can we compare the utility levels of consumers? And whose utility should we compare in a heterogeneous agent framework?
  }
  \end{itemize}
\end{frame}

\begin{frame}{Life-time Utility}
  \begin{itemize}
  \item {
  We calculate the life-time utility of each agent when the economy is in steady state. One time before the policy change and once after the policy change.
  }
  \item {
  Cannot compare two steady states directly. We need to take the transition into account.
  }
  \item {
  Calculating the exact transition path is troublesome. We follow the approximation by Krussel, Mukoyama, and Sahin (2010) which takes care of the idiosyncratic transition.
  }
  \item {
  Just place the agents in the first economy with their current assets into the second economy.
  }
  \end{itemize}
\end{frame}

\begin{frame}{Welfare Analysis}
  \begin{itemize}
  \item {
  Now we can compare the utility level of the same agent before and after the policy change.
  }
  \item {
  Need to come up with a way to quantify the utility differences sensibly.
  }
  \item {
  We calculate a consumption and a cash equivalent of the policy change.
  }
  \end{itemize}
\end{frame}

\begin{frame}{Consumption Equivalent}
  \begin{itemize}

  \item {
  Permanent change of consumption by factor $\Delta$ that increases life-time
  utility by same amount as policy change:
  }
  \end{itemize}
  \begin{equation}
  U^{2}(e,k) = \mathbb{E}\sum_{t=0}^{\infty}\beta^{t}\frac{(c^{1}_{i,t}\Delta)^{1-\sigma}-1}{1-\sigma}\nonumber
  \end{equation}
  \begin{itemize}
  \item {
  If $ \Delta>1 $ agents prefer policy change $ (U^{2}) $, otherwise they do not want it.
  }
  \end{itemize}
\end{frame}

\begin{frame}{Consumption Equivalent}
  \centering \includegraphics[scale=5]{/cons_equiv.pdf}
\end{frame}

@@
